### 2022-03-04 ehoh/ehoh.tex
more

\looseness=-1
Our logic is a variant of the intensional $\lambda$-free Boolean-free
higher-order logic (\lfhol{}) described by Bentkamp et al.\
%, Blanchette, Cruanes, and Waldmann
\cite[Sect.~2]{bbcw-21-lfho}, which could also be called ``applicative
first-order logic.'' In the spirit of FOOL \cite{kotelnikov-16-fool}, we
%% kotelnikov-15-fool
extend the syntax of this by making formulas a special case of terms,
and its semantics by interpreting the Boolean type $o$ as a domain of
cardinality~2. Functional extensionality can be obtained by adding suitable
axioms \cite[Sect.~3.1]{bbcw-21-lfho}.

>>>>

\looseness=-1
Our logic is a variant of the intensional $\lambda$-free Boolean-free
higher-order logic (\lfhol{}) described by Bentkamp et al.\
%, Blanchette, Cruanes, and Waldmann
\cite[Sect.~2]{bbcw-21-lfho}, which could also be called ``applicative
first-order logic.'' In the spirit of FOOL \cite{kotelnikov-16-fool}, we
%% kotelnikov-15-fool
extend the syntax of this logic by making formulas a special case of terms (without adding logical symbols to the signature),
and its semantics by interpreting the Boolean type $o$ as a domain of
cardinality~2. Functional extensionality can be obtained by adding suitable
axioms \cite[Sect.~3.1]{bbcw-21-lfho}.

### 2022-03-04 unif/unif.tex
more

\ourpara{Pragmatic Variant} We structured our procedure so that most of
the unification machinery is contained in the \unifrulename{Bind} step. Modifying
$\mathcal{P}$, we can sacrifice completeness and obtain a pragmatic variant of
the procedure that often performs better in practice. 
%The simplest such modification
%is to limit the number or kind of bindings applied to a single constraint. 
Our preliminary experiments showed that using the mapping $\mathcal{P}_\mathsf{p}$ defined as follows is a reasonable compromise between performance and
completeness:
\begin{itemize}
    \setlength\itemsep{1\jot}
    \item If the constraint is rigid-rigid, $\mathcal{P}_\mathsf{p}(\lambda \overline{x}.
    \, s \unif \lambda \overline{x}. \, t) = \varnothing$.
    \item If the constraint is flex-rigid,
    let 
    $\mathcal{P}_\mathsf{p}(\lambda \overline{x}. \, F \,\overline{s} \unif \lambda \overline{x}. \, a\, \overline{t})$ 
    be 
    \begin{itemize}
        \item an imitation of $a$ for $F$, if $a$ is a constant, and
        \item all Huet-style projections for $F$ if $F$ is not an identification variable.
    \end{itemize}

>>>>

\ourpara{Pragmatic Variant} We structured our procedure so that most of
the unification machinery is contained in the \unifrulename{Bind} step. Modifying
$\mathcal{P}$, we can sacrifice completeness and obtain a pragmatic variant of
the procedure that often performs better in practice. 
%The simplest such modification
%is to limit the number or kind of bindings applied to a single constraint. 
Our preliminary experiments showed that using the mapping $\mathcal{P}_\mathsf{p}$ defined as follows gives good
performance, while finding most useful unifiers:
\begin{itemize}
    \setlength\itemsep{1\jot}
    \item If the constraint is rigid-rigid, $\mathcal{P}_\mathsf{p}(\lambda \overline{x}.
    \, s \unif \lambda \overline{x}. \, t) = \varnothing$.
    \item If the constraint is flex-rigid,
    let 
    $\mathcal{P}_\mathsf{p}(\lambda \overline{x}. \, F \,\overline{s} \unif \lambda \overline{x}. \, a\, \overline{t})$ 
    be 
    \begin{itemize}
        \item an imitation of $a$ for $F$, if $a$ is a constant, and
        \item all Huet-style projections for $F$ if $F$ is not an identification variable.
    \end{itemize}
